Model Search in Relational Domains

### 2016-10-22 decision.tex
meeting changes
some compressing

\subsection{Decision}
A decision $\decisionvar$ is a meet irreducible that refines the
current abstract value $\abs(\trail)$.  Note that meet irreducibles in
relational domains may involve several variables.
%
% For example, a decision in interval 
%domain can be of the form $\langle x R c \rangle$ where 
%$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
%relational domain such as octagon is of the form $ax - by \leq c$, 
%where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
%and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.  
%
Hence, a decision can specify relation between variables, for example 
$\{x \leq y)$.  A decision must always be consistent with respect to 
the trail $\trail$, i.e.\ $\abs(\trail\cdot \decisionvar)\neq \bot$.  
A new decision always increases the decision level by one.

\rmcmt{We call a \emph{singleton} a meet irreducible which does represent a
valid decision ??}.
%
For template polyhedra, singletons are the meet irreducibles
corresponding to a pair of rows $\vec{c}_1,\vec{c}_2$ in matrix
$\mat{C}$ with $\vec{c}_1\vec{\numvar}=-\vec{c}_2\vec{\numvar}$
(i.e.\ \emph{matching} rows) and the corresponding bounds
$\numabsval_1=-\numabsval_1$.
%
A singleton in the interval domain corresponds to a singleton interval
such as $x\leq 1 \wedge -x\leq -1$ For the octagon domain, $1 \leq x-y
\leq 1$ is a singleton.
%
We cannot make decisions for template rows of singletons because there
is no choice left. Similarly, in a SAT solver, we cannot make a
decision on a variable that is already assigned $\true$ or $\false$.
%
Note that for relational domains singletons do not necessarily
concretise to singleton sets of concrete values for the variables
involved.

Given 
%set of variables $\vars$ \pscmt{where from?} and a 
the current abstract value $\abs(\trail)$, $\decide$ heuristically
returns a non-singleton meet irreducible.
%over a set of branching
%variables $\{B\} \subseteq \mathcal{V}$, a bound $c$, and a polarity
%($\leq$ or $\geq$).  For interval domain, $|B|=1$ since an interval
%meet irreducible is defined over a single variable.  For octagons,
%$|B|=2$.  A decision adds a new meet irreducible $m$ to the trail.
%Subsequently, the new state of the solver is defined over $m$ and
%corresponding label information $s=decision$, which is described
%below.
%\[decide: \quad (\mathcal{E},S) \rightarrow (\mathcal{E}(m,s),S) \]

@@

The {\em longest-range} heuristics simply keeps track of the bounds
$\numabsval_l,\numabsval_u$ of matching template rows $\numabsval_l\leq
\vec{c}\vec{x}\leq \numabsval_u$, picks the one with the longest range
$\numabsval_u-\numabsval_l$, and randomly returns the meet irreducible
$\vec{c}\vec{x}\leq
\lfloor\frac{\numabsval_l+\numabsval_u}{2}\rfloor$ or its
complement. This ensures a fairness policy in selecting a variable
since it guarantees that the intervals of meet irreducibles are
uniformly restricted.
%
The {\em random} decision heuristics arbitrarily picks a meet irreducible  
for making decision. \pscmt{uniformly?}
%
%The {\em relational} decision heuristics is only relevant for relational 
%abstract domains.  
%
The {\em berkmin} decision heuristics is inspired 
from decision heuristic used in Berkmin~\cite{eugoldberg07} SAT solver.  
The Berkmin heuristics %is currently implemented for interval constraints only.  
%The heuristic 
keeps track of the activity of %an interval 
meet irreducibles that participate in conflict clauses. 
Based on the most active meet irreducible, ranges a split similar to the {\em longest-range} heuristics.
\Omit {
as well as variables that actively contribute to conflicts but do not explicitly 
appear in conflict clauses.  The set of conflict clauses is 
organised chronologically with the top clause 
as the one deduced in the last.  A branching variable is chosen among the 
free variables whose literals are in the top unsatisfied conflict clause.  
A similar decision heuristics is also implemented in Chaff~\cite{chaff} SAT 
solver, that computes the activity of a variable as the number of occurrences 
of that variable in conflict clauses only. 
}
%
%A bound of a meet irreducible is heuristically chosen to be an
%approximation of the arithmetic average of the current bounds.
%However, the polarity ($\leq$ or $\geq$) of a meet irreducible is
%chosen randomly.

>>>>

\subsection{Decision}
A decision $\decisionvar$ is a meet irreducible that refines the
current abstract value $\abs(\trail)$.  Note that meet irreducibles in
relational domains may involve several variables.
%
% For example, a decision in interval 
%domain can be of the form $\langle x R c \rangle$ where 
%$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
%relational domain such as octagon is of the form $ax - by \leq c$, 
%where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
%and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.  
%
Hence, a decision can specify a relation between variables, for example 
$\{x \leq y)$.  A decision must always be consistent with respect to 
the trail $\trail$, i.e.\ $\abs(\trail\cdot \decisionvar)\neq \bot$.  
A new decision increases the decision level by one.

\rmcmt{We call a \emph{singleton} a meet irreducible which does represent a
valid decision ??}.
%
For template polyhedra, singletons are the meet irreducibles
corresponding to a pair of rows $\vec{c}_1,\vec{c}_2$ in matrix
$\mat{C}$ with $\vec{c}_1\vec{\numvar}=-\vec{c}_2\vec{\numvar}$
(i.e.\ \emph{matching} rows) and the corresponding bounds
$\numabsval_1=-\numabsval_2$.
%
A singleton in the interval domain corresponds to a singleton interval
such as $x\leq 1 \wedge -x\leq -1$ For the octagon domain, $1 \leq x-y
\leq 1$ is a singleton.
%
We cannot make decisions for template rows of singletons because there
is no choice left. Similarly, in a SAT solver, we cannot make a
decision on a variable that is already assigned $\true$ or $\false$.
%
Note that for relational domains singletons do not necessarily
concretise to singleton sets of concrete values for the variables
involved.
%
Given 
%set of variables $\vars$ \pscmt{where from?} and a 
the current abstract value $\abs(\trail)$, $\decide$ heuristically
returns a non-singleton meet irreducible.
%over a set of branching
%variables $\{B\} \subseteq \mathcal{V}$, a bound $c$, and a polarity
%($\leq$ or $\geq$).  For interval domain, $|B|=1$ since an interval
%meet irreducible is defined over a single variable.  For octagons,
%$|B|=2$.  A decision adds a new meet irreducible $m$ to the trail.
%Subsequently, the new state of the solver is defined over $m$ and
%corresponding label information $s=decision$, which is described
%below.
%\[decide: \quad (\mathcal{E},S) \rightarrow (\mathcal{E}(m,s),S) \]

@@

The {\em longest-range} heuristics simply keeps track of the bounds
$\numabsval_l,\numabsval_u$ of matching template rows $\numabsval_l\leq
\vec{c}\vec{x}\leq \numabsval_u$, picks the one with the longest range
$\numabsval_u-\numabsval_l$, and randomly returns the meet irreducible
$\vec{c}\vec{x}\leq
\lfloor\frac{\numabsval_l+\numabsval_u}{2}\rfloor$ or its
complement. This ensures a fairness policy in selecting a variable
since it guarantees that the intervals of meet irreducibles are
uniformly restricted.
%
The {\em random} decision heuristics arbitrarily picks a meet irreducible  
for making decision. 
%
%The {\em relational} decision heuristics is only relevant for relational 
%abstract domains.  
%
The {\em berkmin} decision heuristics is inspired 
from decision heuristic used in Berkmin~\cite{eugoldberg07} SAT solver.  
The Berkmin heuristics %is currently implemented for interval constraints only.  
%The heuristic 
keeps track of the activity of %an interval 
meet irreducibles that participate in conflict clauses. 
Based on the most active meet irreducible, ranges a split similar to the {\em longest-range} heuristics.
\Omit {
as well as variables that actively contribute to conflicts but do not explicitly 
appear in conflict clauses.  The set of conflict clauses is 
organised chronologically with the top clause 
as the one deduced in the last.  A branching variable is chosen among the 
free variables whose literals are in the top unsatisfied conflict clause.  
A similar decision heuristics is also implemented in Chaff~\cite{chaff} SAT 
solver, that computes the activity of a variable as the number of occurrences 
of that variable in conflict clauses only. 
}
%
%A bound of a meet irreducible is heuristically chosen to be an
%approximation of the arithmetic average of the current bounds.
%However, the polarity ($\leq$ or $\geq$) of a meet irreducible is
%chosen randomly.

### 2016-10-22 deductions.tex
some compressing

\section{Abstract Model Search}
%
\Omit {
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & SSA & Octagon \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
SSA &\iff& ((g0 == TRUE) \land \\
    &    & (cond == (x == y)) \land \\
    &    & (g1 == (cond \&\& guard0)) \land \\
    &    & (x' == 1u + x) \land \\
    &    & (x' == 1u + y || !1))
\end{array}$
\end{minipage}
&
\begin{minipage}{3.75cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
C &\iff& ((x' > 1) \land (-x'-y < -2) \land \\
  &    & (-x-x' < -2) \land (y-x' < 0) \land \\                                                                
  &    & (x-x' < 0) \land (y > 0) \land \\
  &    & (x > 0) \land (-x'-y < 0) \land \\
  &    & (x+y > 1) \land (y-x < 1) \land \\
  &    & (x'-y < 2) \land (x-y < 1) \land \\
  &    & (x+y > 0) \land (x+x' > 0) \land \\
  &    & (x'-x < 2))
\end{array}$
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, corresponding SSA and Octagonal Inequalities}
\label{ssa}
\end{figure}
}
%
%    
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKw{return}{return}
\SetKwData{sat}{sat}
\SetKwData{conflict}{conflict}
\SetKwData{unsat}{unsat}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKwFor{Loop}{Loop}{}{}
\SetKw{KwNot}{not}
\begin{small}
\Input{A program in the form of a set of abstract transformers $\abstransset$,
a propagation trail $\trail$, and a reason trail $\reasons$.}
\Output{\sat or \conflict or \unknown}
$\worklist \leftarrow \initworklist_{\propheur}(\abstransset)$ \;
\While{$!\mathit{worklist.empty}()$} 
{
  $\abstransel{\subdomain} \leftarrow \mathit{worklist.pop}()$ \; 
  $\newdeductions \leftarrow \onlynew(\abstransel{\subdomain}(\abs(\trail)))$\;
  \rmcmt{can we avoid onlynew or atleast change the name?}
  \uIf{$\newdeductions = \bot$} {
    $\reasons[\bot] \leftarrow \abstransel{\subdomain}$ \;
    $\mathit{worklist.clear}()$ \;
    \return \conflict \;
  }
  \uElse
  {
%    $\newdeductions=\decomp(\absval)\setminus\decomp(\abs(\trail))$\;
    $\trail \leftarrow \trail \cdot \decomp(\newdeductions)$ \; 
    $\reasons[|\trail|] \leftarrow \abstransel{\subdomain}$ \;
    $\updateworklist_{\propheur}(\newdeductions, \worklist)$ \; 
  }
}
\lIf{$\abs(\trail)$ is $\gamma$-complete} {
  \return \sat;
}
 \return \unknown \;

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Deduction Transformers} \label{sec:abst}
%-------------------------------------------------------------------------------
\Omit{
To make our algorithm efficient, we have to focus the abstract
transformers on performing only the minimally necessary
work. 
}
\rmcmt{The key considerations for building an abstract transformer are 
precision and efficiency.  An efficient transformer is less precise, 
and vice-versa.  Our propagation strategy provides a domain-dependant 
heuristic choice to control these variants.}
%
We thus define a specialised variant of the abstract transformer to compute
deductions w.r.t.\ a given subdomain $\subdomain\subseteq \domain$,
which we call \emph{abstract deduction transformer}.
%
A subdomain contains a chosen subset of the elements in $\domain$ including
$\bot$ and $\top$, \rmcmt{which forms a lattice structure}.  An abstract 
deduction transformer is formally defined as follows. 
\begin{equation}\label{eq:at2}
\abstrans{\domain}{\constraint}^\subdomain(\absval)=\absval\meet_\domain \alpha_\subdomain(\{\val\mid \val\in\gamma_\domain(\absval), \val\models \constraint\})
\end{equation}
For $\subdomain=\domain$, the abstract deduction transformer is identical 
to the abstract transformer defined in Eq.~\ref{eq:abstrans} 
in Section~\ref{sec:domains}.

@@

Algorithm~\ref{Alg:ms} presents the deduction phase $\deduce$ in 
abstract model search procedure.  The input to the algorithm is 
the set of abstract transformers, a propagation trail and a reason 
trail.  Additionally, the procedure $\deduce$ is parameterised with 
a propagation heuristic ($\propheur$). 
%
The algorithm maintains a  {\em worklist}, which is a queue that contains 
abstract deduction transformers.  The propagation heuristics provides two 
functions $\initworklist$ and $\updateworklist$.
The order of the elements in the worklist and the subdomains $\subdomain$
attached \rmcmt{or associated} to each abstract deduction transformers 
\rmcmt{($\abstransel{\subdomain}$)} determine the propagation strategy 
(forward, backward, multi-way).
%
The {\em forward} propagation strategy initialises the worklist with
abstract deduction transformers that contains constants in the
right-hand side and the subdomain is constructed via $\makesubdomain$
from variables in left-hand side of the equality constraints
originating from the assignment statements in the program.
%
The {\em backward} propagation strategy intialises the worklist 
with the assertions and the subdomain is constructed from the 
right-hand side variables.
%
The {\em multi-way} propagation strategy initialises the worklist 
with set of all transformers and each \rmcmt{each or the corresponding ?} 
subdomains contains the variables occurring in the respective transformers.
%
Depending on the propagation heuristics, $\updateworklist$ adds
abstract deduction transformers to the worklist that contain variables
that appear in $\newdeductions$, and it updates the subdomains of
the abstract deduction transformers in the worklist 
to include the variables in $\newdeductions$.
%
The function
$\onlynew(\absval)=\bigsqcap(\decomp(\absval)\setminus\decomp(\abs(\trail)))$
is used to filter out all meet irreducibles that are already on the trail
in order to obtain only new deductions when applying the abstract deduction transformer.
%
\Omit{
If $\bot$ is deduced we return \textsf{conflict}.
Otherwise, when eventually a fixed point has been reached, i.e.\ the worklist is empty, then the abstract value $\abs(\trail)$ is checked whether it is 
$\gamma$-complete~\cite{dhk2013-popl}. It is $\gamma$-complete if all concrete values in $\gamma(\abs(\trail))$ satisfy $\formula$.
Otherwise, the algorithm returns \textsf{unknown} and the 
model search procedure makes a new decision.    
}
\rmcmt{If $\abstransel{\subdomain}$ deduce $\bot$, then 
the procedure $\mathit{deduce}$ returns \textsf{conflict}.
Otherwise, when a fixed point is reached, i.e.\ 
the worklist is empty, then the abstract value $\abs(\trail)$ is checked 
for $\gamma$-completeness~\cite{dhk2013-popl}.  If it is indeed 
$\gamma$-complete, then $\mathit{deduce}$ returns \sat.  Otherwise, the 
algorithm returns \textsf{unknown} and the abstract model search 
procedure makes a new decision.    
}

>>>>

\section{Abstract Model Search}
%
\Omit {
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & SSA & Octagon \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
SSA &\iff& ((g0 == TRUE) \land \\
    &    & (cond == (x == y)) \land \\
    &    & (g1 == (cond \&\& guard0)) \land \\
    &    & (x' == 1u + x) \land \\
    &    & (x' == 1u + y || !1))
\end{array}$
\end{minipage}
&
\begin{minipage}{3.75cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
C &\iff& ((x' > 1) \land (-x'-y < -2) \land \\
  &    & (-x-x' < -2) \land (y-x' < 0) \land \\                                                                
  &    & (x-x' < 0) \land (y > 0) \land \\
  &    & (x > 0) \land (-x'-y < 0) \land \\
  &    & (x+y > 1) \land (y-x < 1) \land \\
  &    & (x'-y < 2) \land (x-y < 1) \land \\
  &    & (x+y > 0) \land (x+x' > 0) \land \\
  &    & (x'-x < 2))
\end{array}$
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, corresponding SSA and Octagonal Inequalities}
\label{ssa}
\end{figure}
}
%
%    
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKw{return}{return}
\SetKwData{sat}{sat}
\SetKwData{conflict}{conflict}
\SetKwData{unsat}{unsat}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKwFor{Loop}{Loop}{}{}
\SetKw{KwNot}{not}
\begin{small}
\Input{A program in the form of a set of abstract transformers $\abstransset$,
a propagation trail $\trail$, and a reason trail $\reasons$.}
\Output{\sat or \conflict or \unknown}
$\worklist \leftarrow \initworklist_{\propheur}(\abstransset)$ \;
\While{$!\mathit{worklist.empty}()$} 
{
  $\abstransel{\subdomain} \leftarrow \mathit{worklist.pop}()$ \; 
  $\absval \leftarrow \abstransel{\subdomain}(\abs(\trail))$\;
  \uIf{$\absval = \bot$} {
    $\reasons[\bot] \leftarrow \abstransel{\subdomain}$ \;
    $\mathit{worklist.clear}()$ \;
    \return \conflict \;
  }
  \uElse
  {
    $\newdeductions=\onlynew(\absval)$\;
%    $\newdeductions=\decomp(\absval)\setminus\decomp(\abs(\trail))$\;
    $\trail \leftarrow \trail \cdot \decomp(\newdeductions)$ \; 
    $\reasons[|\trail|] \leftarrow \abstransel{\subdomain}$ \;
    $\updateworklist_{\propheur}(\worklist, \newdeductions, \abstransel{\subdomain},  \abstransset)$ \; 
  }
}
\lIf{$\abs(\trail)$ is $\gamma$-complete} {
  \return \sat;
}
 \return \unknown \;

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Deduction Transformers} \label{sec:abst}
%-------------------------------------------------------------------------------
\Omit{
To make our algorithm efficient, we have to focus the abstract
transformers on performing only the minimally necessary
work. 
}
\rmcmt{The key considerations for building an abstract transformer are 
precision and efficiency.  An efficient transformer is less precise, 
and vice-versa.  Our propagation strategy provides a domain-dependant 
heuristic choice to control these variants.}
%
We thus define a specialised variant of the abstract transformer to compute
deductions w.r.t.\ a given subdomain $\subdomain\subseteq \domain$,
which we call \emph{abstract deduction transformer}.
%
A subdomain contains a chosen subset of the elements in $\domain$ including
$\bot$ and $\top$, \rmcmt{which forms a lattice structure}.  An abstract 
deduction transformer is formally defined as follows. 
\begin{equation}\label{eq:at2}
\abstrans{\domain}{\constraint}^\subdomain(\absval)=\absval\meet_\domain \alpha_\subdomain(\{\val\mid \val\in\gamma_\domain(\absval), \val\models \constraint\})
\end{equation}
For $\subdomain=\domain$, the abstract deduction transformer is identical 
to the abstract transformer defined in Eq.~(\ref{eq:abstrans})
in Section~\ref{sec:domains}.

@@

Algorithm~\ref{Alg:ms} presents the deduction phase $\deduce$ in 
abstract model search procedure.  The input to the algorithm is 
the set of abstract transformers, a propagation trail and a reason 
trail.  Additionally, the procedure $\deduce$ is parameterised with 
a propagation heuristic ($\propheur$). 
%
The algorithm maintains a  {\em worklist}, which is a queue that contains 
abstract deduction transformers.  The propagation heuristics provides two 
functions $\initworklist$ and $\updateworklist$.
The order of the elements in the worklist and the subdomains $\subdomain$
attached \rmcmt{or associated} to each abstract deduction transformers 
\rmcmt{($\abstransel{\subdomain}$)} determine the propagation strategy 
(forward, backward, multi-way).
%
The {\em forward} propagation strategy initialises the worklist with
abstract deduction transformers that contains constants in the
right-hand side and the subdomain is constructed via $\makesubdomain$
from variables in left-hand side of the equality constraints
originating from the assignment statements in the program.
%
The {\em backward} propagation strategy intialises the worklist 
with the assertions and the subdomain is constructed from the 
right-hand side variables.
%
The {\em multi-way} propagation strategy initialises the worklist 
with set of all transformers and each \rmcmt{each or the corresponding ?} 
subdomains contains the variables occurring in the respective transformers.
%
Depending on the propagation heuristics, $\updateworklist$ adds
abstract deduction transformers to the worklist that contain variables
that appear in $\newdeductions$, and it updates the subdomains of
the abstract deduction transformers in the worklist 
to include the variables in $\newdeductions$.
%
The function
$\onlynew(\absval)=\bigsqcap(\decomp(\absval)\setminus\decomp(\abs(\trail)))$
is used to filter out all meet irreducibles that are already on the trail
in order to obtain only new deductions when applying the abstract deduction transformer.
%
\Omit{
If $\bot$ is deduced we return \textsf{conflict}.
Otherwise, when eventually a fixed point has been reached, i.e.\ the worklist is empty, then the abstract value $\abs(\trail)$ is checked whether it is 
$\gamma$-complete~\cite{dhk2013-popl}. 
%
\begin{definition} 
\pscmt{reformulate} An abstract value $\absval$ is $\gamma$-complete if all concrete values in 
$\gamma(\absval)$ satisfy $\formula$.  
\end{definition}
%
It is $\gamma$-complete if all concrete values in $\gamma(\abs(\trail))$ satisfy $\formula$.
Otherwise, the algorithm returns \textsf{unknown} and the 
model search procedure makes a new decision.    
}
\rmcmt{If $\abstransel{\subdomain}$ deduce $\bot$, then 
the procedure $\mathit{deduce}$ returns \textsf{conflict}.
Otherwise, when a fixed point is reached, i.e.\ 
the worklist is empty, then the abstract value $\abs(\trail)$ is checked 
for $\gamma$-completeness~\cite{dhk2013-popl}.  If it is indeed 
$\gamma$-complete, then $\mathit{deduce}$ returns \sat.  Otherwise, the 
algorithm returns \textsf{unknown} and the abstract model search 
procedure makes a new decision.    
}

### 2016-10-22 paper.tex
typo
some compressing

\institute{University of Oxford, UK \and University of Sussex, UK \\
\email{\{rajdeep.mukherjee,kroening,tom.melham\}@cs.ox.ac.uk},
\email{p.schrammel@sussex.ac.uk}}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalisation
of the well-known CDCL algorithm that is used in SAT solvers.
%
\Omit {  ACDCL alternates between a model search, which
performs over-approximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
}
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in satisfiability 
solvers can be rather easily lifted from the Boolean lattice to other 
non-relational domains, application to relational domains is 
challenging because of relational properties of deductions.
%
In this paper, we present the non-trivial liftings of the model search and
conflict analysis algorithms for relational abstract domains.  We have
implemented these algorithms inside the 2LS verification tool and
instantiated our analyser over a template polyhedra domain to check safety
properties of C programs.  We~evaluate the performance of our analyser in
comparison with program verifiers that uses propositional-level solvers and
a static analysis tool.
%
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
We observe a reduction of two orders of magnitude in the number of 
decisions and conflict analyses compared to a satisfiability 
solver and higher precision compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}

>>>>

\institute{University of Oxford, UK \and University of Sussex, UK \\
%\email{\{rajdeep.mukherjee,kroening,tom.melham\}@cs.ox.ac.uk},
%\email{p.schrammel@sussex.ac.uk}
}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalisation
of the well-known CDCL algorithm that is used in SAT solvers.
%
\Omit {  ACDCL alternates between a model search, which
performs over-approximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
}
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in SAT 
solvers can be rather easily lifted from the Boolean lattice to other 
non-relational domains, application to relational domains is 
challenging because of relational properties of deductions.
%
In this paper, we present the non-trivial liftings of the model search and
conflict analysis algorithms for relational abstract domains.  We have
implemented these algorithms inside the 2LS verification tool and
instantiated our analyser over a template polyhedra domain to check safety
properties of C programs.  We~evaluate the performance of our analyser in
comparison with program verifiers that use propositional-level solvers and
a static analysis tool.
%
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
We observe a reduction of two orders of magnitude in the number of 
decisions and conflict analyses compared to a SAT 
solver and higher precision compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}
